\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
% \renewcommand{\itemmarker}{{\small\textbullet}}
% \renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Erfan Zafarani}
\tagline{CompSci student looking to break into the tech space.}

\personalinfo{
  \email{erfan.zafarani.20@ucl.ac.uk}
  \phone{+44 74 11 049904}
  \location{33 Empire House, London, NW9 5ZG}
%  \homepage{robertonoel.com/}
  \linkedin{linkedin.com/in/erfanzafarani/}
  \github{github.com/TketEZ/} 
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.

\cvsection[sidebar1]{Education}
\cvevent{MSc Computer Science}{University College London}{ Sep 2020 - Sep 2021}{London, UK}
\begin{itemize}
\item Electives in: Machine Learning, Software Engineering, Interaction Design \\
\end{itemize}
\divider \\
\cvevent{BSc Industrial Economics}{University of Nottingham}{ Sep 2015 - Aug 2018}{Nottingham, UK}
\begin{itemize}
\item Studied abroad in Ningbo, China. \\
\item Leadership positions: Team leader in Enactus Nottingham; Vice president of AIESEC Nottingham \\
\end{itemize}

\cvsection{Experience}
\cvevent{Sales Negotiator}{Douglas \& Gordon}{September 2019 -- August 2020}{London, UK}
\begin{itemize}
\item Built strong relationships with potential buyers (evidenced by multiple five* Google Reviews) and sellers, securing a new listing for our office which was subsequently sold.
\item Managed time independently across multiple responsibilities such as viewings, lead generation, deal chasing and communicating with customers. 
\item Highest number of Google Reviews across the central division in August. 
\smallskip
\end{itemize}
\divider \\
\cvevent{Client Solutions Associate - Intern}{FactSet}{Oct 2018 -- Feb 2019}{London, UK}
\begin{itemize}
\item Serviced accounts responsible for \$2.5M of annual subscription value within 5 months of starting, showing the ability to learn quickly and implement even faster. 
\smallskip
\item Built relationships with people at all levels of seniority across different departments and companies. Leveraged relationships to increase brand awareness and uncover sales opportunities. 
\end{itemize}
\cvsection{Languages}
\cvskill{English}{5}
\cvskill{Farsi}{5}
\cvskill{Spanish}{4}

\clearpage

\end{document}
